\section{Goal of simulations}
The ultimate goal of this study was to develop a understanding and ability to preform parametric
studies of the flows for ACS rockets, that studied the forces and torques depening on the angle of 
attack, angle of sideslip and angles of conards. This ability would be then used to get aerodynamic 
coefficients for a specific rocket models, like Sterink 1.5 or Sternik 2.0 and then for project 
Unite with Sweedish team.


\section{Software used}
Models were created in Solidworks and then exported to the following programs for flow simulations.
For Solidworks we could simply use it right away, but for Ansys Fluent we had to export 
it to .step file format.\\\\
During the course of this project, the following programs were used for flow simulations:
\begin{enumerate}
    \item Solidworks Flow Simulations
    \item Ansys Fluent
    \item OpenFOAM
\end{enumerate}
Solidworks Flow Simulations was used for the initial simulations, as it was the easiest to use and
the fastest to set up. It was used to get a general idea of the flow around the rocket and was 
simple in setting up parametric studies. Few parametric studies were done in Solidworks Flow 
Simulations that were analyzed and many graphs were created in hope to get a better understanding 
of processes that are happening and to check whether the results make any sense. However, many
results were not as expected and the decision was made to switch to Ansys Fluent, to chceck if the 
Simulations are of any value.\\\\
Ansys Fluent was used to get more accurate results and to check if the results from Solidworks
Flow Simulations were correct. However it proved to be a lot harder to used then Solidworks and
we are currently still working on getting the results from it.\\\\
OpenFOAM was only used by Jacek to get some results for the Sterink 1.5 model, but after some meshes
and learning how to use it, it was decided to not use it for the rest of the project, since rest 
of the team was not familiar with it and it was not worth the time to learn it and Jacek had to 
focus on other stuff.